### 2017-04-17 paper/oopsla17-submission/conclusion.tex
more minor

We have presented \toolname, which
combines modern statistical methods
with domain-specific feature engineering
to open the door to a new data-driven
path to precise error localization,
that significantly outperforms the
state of the art on a new benchmark
suite comprising 4500 student programs.
%
%%% RJNUKEDME   \toolname
%%% RJNUKEDME   translates pairs of
%%% RJNUKEDME   blame-labeled ill-typed
%%% RJNUKEDME   programs into bags-of-abstracted-terms,
%%% RJNUKEDME   and then trains a classifier
%%% RJNUKEDME   to predict whether a feature vector
%%% RJNUKEDME   should get a blame label.
%%% RJNUKEDME   % that
%%% RJNUKEDME   % predicts the value of the
%%% RJNUKEDME   % whether a feature vector gets
%%% RJNUKEDME   % a blame label.
%%% RJNUKEDME   %
%%% RJNUKEDME   Given a new ill-typed program,
%%% RJNUKEDME   we extract its bag-of-abstracted-terms
%%% RJNUKEDME   to compute the blame label for each
%%% RJNUKEDME   term and rank the predictions based
%%% RJNUKEDME   on the model's confidence, to select
%%% RJNUKEDME   the top 1--3 blame assignments to
%%% RJNUKEDME   present to the user.
%%% RJNUKEDME
%%% RJNUKEDME   We have evaluated our approach with
%%% RJNUKEDME   five different classifiers on a suite
%%% RJNUKEDME   of over 4,500 student programs.
%%% RJNUKEDME   %
%%% RJNUKEDME   We found that while machine learning
%%% RJNUKEDME   over syntactic features of each term in isolation
%%% RJNUKEDME   performs worse than existing
%%% RJNUKEDME   purely constraint based approaches, % (\eg \ocaml, \sherrloc),
%%% RJNUKEDME   augmenting the data with a single feature corresponding to
%%% RJNUKEDME   the type error slice brings our
%%% RJNUKEDME   classifiers up to par with the state of the art,
%%% RJNUKEDME   and further augmenting the data with
%%% RJNUKEDME   features of an expression's parent and children
%%% RJNUKEDME   allows our classifiers to outperform
%%% RJNUKEDME   the state of the art by 18 percentage points.

>>>>

We have presented \toolname, which
combines modern statistical methods
with domain-specific feature engineering
to open the door to a new data-driven
path towards precise error localization,
significantly outperforming the
state of the art on a new benchmark
suite comprising 4,500 student programs.
%
%%% RJNUKEDME   \toolname
%%% RJNUKEDME   translates pairs of
%%% RJNUKEDME   blame-labeled ill-typed
%%% RJNUKEDME   programs into bags-of-abstracted-terms,
%%% RJNUKEDME   and then trains a classifier
%%% RJNUKEDME   to predict whether a feature vector
%%% RJNUKEDME   should get a blame label.
%%% RJNUKEDME   % that
%%% RJNUKEDME   % predicts the value of the
%%% RJNUKEDME   % whether a feature vector gets
%%% RJNUKEDME   % a blame label.
%%% RJNUKEDME   %
%%% RJNUKEDME   Given a new ill-typed program,
%%% RJNUKEDME   we extract its bag-of-abstracted-terms
%%% RJNUKEDME   to compute the blame label for each
%%% RJNUKEDME   term and rank the predictions based
%%% RJNUKEDME   on the model's confidence, to select
%%% RJNUKEDME   the top 1--3 blame assignments to
%%% RJNUKEDME   present to the user.
%%% RJNUKEDME
%%% RJNUKEDME   We have evaluated our approach with
%%% RJNUKEDME   five different classifiers on a suite
%%% RJNUKEDME   of over 4,500 student programs.
%%% RJNUKEDME   %
%%% RJNUKEDME   We found that while machine learning
%%% RJNUKEDME   over syntactic features of each term in isolation
%%% RJNUKEDME   performs worse than existing
%%% RJNUKEDME   purely constraint based approaches, % (\eg \ocaml, \sherrloc),
%%% RJNUKEDME   augmenting the data with a single feature corresponding to
%%% RJNUKEDME   the type error slice brings our
%%% RJNUKEDME   classifiers up to par with the state of the art,
%%% RJNUKEDME   and further augmenting the data with
%%% RJNUKEDME   features of an expression's parent and children
%%% RJNUKEDME   allows our classifiers to outperform
%%% RJNUKEDME   the state of the art by 18 percentage points.
